Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-09-30 prop_letter.tex
prop_letter.tex \section{Gleason} Keep reconstructing...

\noindent Since $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$ clearly
satisfies Eqs.~(\ref{eq:QIVPM-constraints}), the condition that
needs to be checked is Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$, it
is easy to verify that
\begin{equation}
\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\,.\label{eq:iota-add}
\end{equation}
This implies Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
when $P_{0}$ and $P_{1}$ are orthogonal. When $P_{0}$ and $P_{1}$
are not orthogonal on a three-dimensional Hilbert space, we have two
possibilities:
\begin{itemize}
\item Their complements are orthogonal so that we can apply Eq.~(\ref{eq:iota-add})
on their complements.
\item One of them projects onto a subspace of what the other one projects
onto.
\end{itemize}
\noindent No matter which case holds, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
can be deduced easily. Therefore, $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
is indeed a QIVPM.

@@

Our framework allows us to generalize the above theorem to Born QIVPMs~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$:
The collection of states consistent $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
gets closer and closer to $\rho$ as the intervals get narrower and
narrower, eventually collapsing to $\rho$ when the intervals become
infinitely precise real numbers covering the real line. To state this
result, we need to introduce a notion of distance between two states~$\rho$
and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199}.
By replacing the QIVPM~$\bar{\mu}$ in Thm.~\ref{cor:Gleason's}
by a Born QIVPM~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$, we obtain
the following theorem that estimates the states consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$.

\noindent If a state~$\rho'$ is consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
the difference between their Born quantum probabilities on any 1-dimensioal
projector~$\proj{\psi}$, $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$,
must be bounded by $1/n$ which implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$
by definition. For example, Table~\ref{tab:Compute-the-QIVPM} shows
that $\rho_{0}$ is consistent with $\left[\mu_{\rho_{1}}^{\mathrm{B}}\right]_{2}$
and $\rho_{1}$ is consistent with $\left[\mu_{\rho_{0}}^{\mathrm{B}}\right]_{2}$
both on every projectors in $\events_{C}$. Indeed, they are consistent
with each other on every projectors in $\events$ that implies $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{2}$
by Thm.~\ref{thm:Finite-precision-Gleason}. This is true because
the exact value of $\left\Vert \rho_{0}-\rho_{1}\right\Vert $ is
$\frac{1}{24}$~\citep{544199}.

>>>>

\noindent To prove that $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
is a QIVPM, it is sufficient to check Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$, it
is easy to verify that
\begin{equation}
\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\,.\label{eq:iota-add}
\end{equation}
This implies Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
when $P_{0}$ and $P_{1}$ are orthogonal. When $P_{0}$ and $P_{1}$
are not orthogonal on a three-dimensional Hilbert space, we have two
possibilities:
\begin{itemize}
\item Their complements are orthogonal so that we can apply Eq.~(\ref{eq:iota-add})
on their complements.
\item One of them projects onto a subspace of what the other one projects
onto.
\end{itemize}
\noindent Both cases deduce Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
easily so that $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$ is indeed
a QIVPM.

The collection of states consistent $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
gets closer and closer to $\rho$ as the intervals get narrower and
narrower, eventually collapsing to $\rho$ when the intervals become
infinitely precise real numbers covering the real line. To state this
result, we need to introduce a notion of distance between two states~$\rho$
and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199}.
By replacing the QIVPM~$\bar{\mu}$ in Thm.~\ref{cor:Gleason's}
by a Born QIVPM~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$, we obtain
the following theorem that estimates the states consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$.

\noindent If a state~$\rho'$ is consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$,
the difference between their Born quantum probabilities on any 1-dimensioal
projector~$\proj{\psi}$, $\left|\mu_{\rho}^{\mathrm{B}}\left(\proj{\psi}\right)-\mu_{\rho'}^{\mathrm{B}}\left(\proj{\psi}\right)\right|$,
must be bounded by $1/n$ which implies $\left\Vert \rho-\rho'\right\Vert \le\frac{1}{n}$
by definition.

@@

Our framework allows us to generalize the above theorem to Born QIVPMs~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$:

\noindent  For example, Table~\ref{tab:Compute-the-QIVPM} shows
that $\rho_{0}$ is consistent with $\left[\mu_{\rho_{1}}^{\mathrm{B}}\right]_{2}$
and $\rho_{1}$ is consistent with $\left[\mu_{\rho_{0}}^{\mathrm{B}}\right]_{2}$
both on every projectors in $\events_{C}$. Indeed, they are consistent
with each other on every projectors in $\events$ that implies $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{2}$
by Thm.~\ref{thm:Finite-precision-Gleason}. This is true because
the exact value of $\left\Vert \rho_{0}-\rho_{1}\right\Vert $ is
$\frac{1}{24}$~\citep{544199}.
